Representation Project

### 2024-12-09 paper.qmd
fix word link

  <a class="btn btn-warning btn-sm mb-1" target="_blank" href="/manuscript/output/manuscript.docx">
  <iconify-icon inline="" icon="fa6-solid:file-arrow-down"></iconify-icon> &ensp;docx <small>(download)</small>
  </a>

>>>>

  <a class="btn btn-warning btn-sm mb-1" target="_blank" href="/manuscript/output/manuscript.docx">
  <i class="fa-solid fa-file-word"></i>&ensp;docx <small>(download)</small>
  </a>
